Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-15 Paper.tex
Switch Tx and Uncles

The other two components in the block are simply a list of uncle block headers (of the same format as above) and a list of the transactions (as defined previously). Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (H, \mathbf{U}, \mathbf{T})
\end{equation}

@@

\section{Recursive Length Prefix}\label{app:rlp}
This is a method for encoding arbitrarily structured binary data (byte arrays).

@@

\begin{verbatim}
[
  blockHeader: [...]
  uncleList: [ [...], [...], ... ]
  txList: [ [...], [...], ... ]
]
\end{verbatim}

>>>>

The other two components in the block are simply a list of uncle block headers (of the same format as above) and a list of the transactions (as defined previously). Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (H, \mathbf{T}, \mathbf{U})
\end{equation}

@@

\section{Recursive Length Prefix}\label{app:rlp}
This is a serialisation method for encoding arbitrarily structured binary data (byte arrays). Within RLP, integers are specified as the byte array equal to the big-endian representation of the value. Thus we may define the notation of a tree structure $\mathbf{t}$:

\begin{equation}
\mathbf{t}
\end{equation}

We define the function $\mathtt{\tiny RLP}$ that maps from an arbitrarily structured tree whose leaves are byte arrays into a single byte array.

@@

\begin{verbatim}
[
  blockHeader: [...]
  txList: [ [...], [...], ... ]
  uncleList: [ [...], [...], ... ]
]
\end{verbatim}
